\documentclass[a4paper, 11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{geometry}

\setlength{\voffset}{-0.75in}
\setlength{\headsep}{5pt}
\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\@title}

  \@author
\end{flushleft}\egroup
}
\makeatother


\title{Siraj Singh Sandhu}

\author{%
Department of Computer Science and Engineering\\
Indian Institute of Technology Kanpur, India\\
{\it Email:sssandhu@iitk.ac.in}
}


\begin{document}

\maketitle

\noindent\hrule % hrule -> horizontal line
\vspace{1mm}
\noindent\hrule

% \noindent\textit{This paragraph is a brief about myself and my life objectives.}
\noindent
I am a second year undergraduate student with an interest in Applied Probability, Data Science and Machine Learning. I am also very keen on debates on public and foreign policy, including geo-political relations, especially in the Middle East.

\noindent\hrule
\vspace{1mm}
\noindent\hrule
\vspace{5mm}

\noindent\textbf{Education}
\begin{flushleft} % flushleft -> left aligned
\begin{tabular}{ |c|c|c|c| }
\hline % --> row separating line
Matriculation & 2014 & St. John's High School, Chandigarh & 10 CGPA\\
\hline
Intermediate & 2016 & Sri Guru Gobind Singh Sr. Sec. School & 91.8\% \\
\hline
BTech & 2016- & Indian Institute of Technology, Kanpur & 8.91 CGPA \\ 
\hline
\end{tabular}
\end{flushleft}

\vspace{3mm}
\noindent\textbf{Course Details}
\begin{flushleft}
\begin{tabular}{ |c|c|c| }
\hline
\textbf{Semester} & \textbf{Total Credits} & \textbf{Highlights}\\
\hline
Aug 2016 - Dec 2016 & 14 & ECO101\\
Aug 2016 - Dec 2016 & 14 & ESC101\\
Jan 2017 - Apr 2017 & 11 & MTH102\\
Aug 2017 - Dec 2017 & 9 & CS201\\
Aug 2017 - Oct 2017 & 5 & CS203\\
Jan 2018 - Apr 2018 & 11 & MSO203\\
Jan 2018 - Apr 2018 & 12 & ESO207\\
\hline
\end{tabular}
\end{flushleft}
\vspace{3mm}

\noindent\textbf{Skills}

\vspace{1mm}

\noindent Programming Languages :\hspace{2mm} C, C++, Python

\vspace{3mm}

\noindent\textbf{Projects}

\vspace{2mm}
1.{\it Depression Therapy Chatbot:}  Implemented a retrieval-based, short conversation, closed domain chatbot using a Dual Encoder LSTM
network and trained on the Ubuntu Dialog Corpus (UDC). Employed LSTM and word embeddings of prior context and responses to generate a prediction, applied the
sigmoid function to obtain the required probability distribution of sampled responses.

\vspace{1mm}

% {\it ..... } alternative for |textit{ ..... }

2.{\it Competitive Machine Learning, Digit Recognition \& Text Summarization:}  Studied and implemented common Machine Learning Algorithms and Techniques. Solved the following problems on Kaggle: Titanic, Machine Learning from Disaster and Bag of Words using Scikit-Learn. Performed Recognition of Handwritten Digits on MNIST dataset using feed-forward neural networks, achieving 96\% accuracy. Implemented RSS newsfeed summarizer using NLTK, Gensim (Word2Vec), Tf-Idf Algorithm and Networkx Package (Page Rank).

\vspace{310mm}

\noindent\textbf{Awards and Achievements}

\vspace{1.5mm}

\indent{-AIR 179 in JEE Advanced - 2016}

\vspace{1.5mm}

\indent{-NTSE Scholar}
\vspace{3mm}
 
 
\noindent\textbf{Hobbies}

\vspace{1.5mm}

\indent{-Sports: Basketball}

\vspace{1.5mm}

\indent{-Quizzing}

\vspace{1.5mm}

\indent{-Public Speaking/Oratory}

\end{document}
